```{r envSetup, include = FALSE, echo = FALSE}
knitr::opts_chunk$set(
    echo = TRUE,
    message = FALSE,
    warning = FALSE,
    out.width = "65%",
    fig.align = "center",
    comment = ">"
    )
```



```{r, include = FALSE, echo = FALSE}
##library(tidyverse)
library(corrr)
library(psych)
library(lavaan)
#library(kableExtra)
library(dplyr)
library(tidyr)
library(ggplot2)
library(survey)
library(haven)
library(rempsyc)
library(broom)
library(report)
library(effectsize)
library(aod)
library(readr)
#library(tidymodels)
library(stargazer)
library(forcats)
library(ggcorrplot)
library(caret)
library(knitr)
library(ROCR)
library(jtools)
#=library(car)
library(xtable)
#library(texreg)
#library(svyVGAM)
library(glmnet)
library(ggpubr)
library(lme4)
library(nlme)
library(weights)
library(miscTools)
library(systemfit)
library(multcomp)
require(ggplot2)
require(GGally)
require(reshape2)
#require(compiler)
#require(parallel)
#require(boot)
require(lattice)
library(HLMdiag)
#library(DHARMa)
library(car) #for the Levene test which we will not discuss here
library(Matrix)
library(brms)
library(margins)
library(performance)
library(ggnewscale)
library(ggeffects)
library(bayestestR) # for hypothesis testing
library(brmsmargins)
library(ggeffects)
library(marginaleffects)
library(effects)
library(margins)
library(modelr)
library(plm)
library(effectsize)
library(aod)
library(readr)
library(tidymodels)
library(stargazer)
library(forcats)
library(ggcorrplot)
library(caret)
library(knitr)
library(ROCR)
library(jtools)
#=library(car)
library(xtable)
#library(texreg)
#library(svyVGAM)
library(glmnet)
library(ggpubr)
library(foreign)
library(AER)
library(lme4)
library(brms)
library(glmnet)
library(ggpubr)
library(formatR)
library(pglm)
library(acqr)
```


```{r}
df <- read.csv("IOS_app_information.csv", header = T)
```

```{r}
glimpse(df)
```
```{r}
df$name_in_icon <- as.factor(df$name_in_icon)  
df$most_frequent_stars <- as.factor(df$most_frequent_stars) 
df$second_most_frequent_stars <- as.factor(df$second_most_frequent_stars)
df$third_most_frequent_stars <- as.factor(df$third_most_frequent_stars) 
df$apple_watch <- as.factor(df$apple_watch)
df$apple_wallet <- as.factor(df$apple_wallet)
```


```{r}
View(df)
```

```{r}
df2 <- df
```

```{r}
df2 <- df2 %>% mutate(
    weighted_average = avg_rating * num_ratings
)
```


```{r}
df2 %>% dplyr::select(Bank, weighted_average) %>% arrange(desc(weighted_average))
```

```{r}
df2 %>% dplyr::select(Bank, avg_rating) %>% arrange(desc(avg_rating))
```

```{r}
df2 %>% dplyr::select(Bank, latest_version_rate) %>% arrange(desc(latest_version_rate))
```


```{r}
df2 <- df2 %>% mutate(latest_version_weightedAvg = latest_version_numRating * latest_version_rate)
df2 %>% dplyr::select(Bank, latest_version_weightedAvg) %>% arrange(desc(latest_version_weightedAvg))

```

```{r}
df2 %>% dplyr::select(Bank, latest_version_numRating) %>% arrange(desc(latest_version_numRating))

```

```{r}
df2 %>% dplyr::select(chart_rank, avg_rating, num_ratings, weighted_average,latest_version_rate, latest_version_numRating,latest_version_weightedAvg, age_min, num_pictures_iphone, num_pictures_ipad, num_pictures_watch, size, most_frequent_stars, second_most_frequent_stars, third_most_frequent_stars) %>% psych::describe()
```


```{r}
glimpse(df2)
```

```{r}
ggplot(df2, 
       aes(x = latest_version_weightedAvg, y = weighted_average)) + 
    geom_point(size = 3) + 
    geom_text(aes(label = Bank), vjust = -1, hjust = 0.5, size = 3) +  
    geom_hline(yintercept = mean(df2$weighted_average), linetype = "dashed", color = "red", size = 1, alpha = 0.6) + 
    geom_vline(xintercept = mean(df2$latest_version_weightedAvg), linetype = "dashed", color = "blue", size = 1, alpha = 0.7) + 
    theme_minimal() +
    labs(y = "Weighted Average Rating (K)", x = "Weighted Average Rating (Latest Version), K") + 
    scale_y_continuous(labels = function(x) x / 1000,  # Divide by 100,000 to adjust the unit
                       breaks = scales::pretty_breaks(n = 10)) + 
    scale_x_continuous(labels = function(x) x / 1000,  
                       breaks = scales::pretty_breaks(n = 10)) + 
    annotate("text", x = 35000, y = mean(df2$weighted_average), 
           label = paste("Weighted Average Rating", round(mean(df2$weighted_average), 2)), 
           hjust = -0.1, vjust = -1.5, color = "red", fontface = "bold") + 
     annotate("text", x = 16000, y = 5000000, 
           label = paste("Latest W Average Rating", round(mean(df2$latest_version_weightedAvg), 2)), 
           hjust = -0.1, vjust = -1.5, color = "blue", fontface = "bold", angle = -90)
```

```{r}
library(scales)  # For the label formatting functions
```

```{r, fig.height=5}
ggplot(df2, 
       aes(x = latest_version_rate, y = avg_rating, size = num_ratings)) + 
    geom_point(alpha = 0.7) + 
    geom_text(aes(label = Bank), vjust = -2, fontface = "bold", hjust = 0.5, size = 3) +  
    geom_hline(yintercept = mean(df2$avg_rating), linetype = "dashed", color = "red", size = 1) + 
    geom_vline(xintercept = mean(df2$latest_version_rate), linetype = "dashed", color = "blue", size = 1) + 
    theme_minimal() +
    labs(y = "Overall Average Rating", x = "Latest Version Average Rating", size = "Number of Ratings") + 
    
    annotate("text", x = 1, y = mean(df2$avg_rating), 
           label = paste("Average Rating", round(mean(df2$avg_rating), 2)), 
           hjust = -0.1, vjust = -1.5, color = "red", fontface = "bold") + 
    
    annotate("text", x = mean(df2$latest_version_rate) - 0.25, y = 5, 
           label = paste("Latest Version Avg.Rating", round(mean(df2$latest_version_rate), 2)), 
           hjust = -0.1, vjust = -1.5, color = "blue", fontface = "bold", angle = -90) + 
    
    scale_size_continuous(range = c(3, 10), labels = label_number(scale_cut = cut_short_scale()))  #CHAT GPT 

```





```{r}
avg_rating_mean <- mean(df2$avg_rating, na.rm = TRUE)

ggplot(data    = df2,
       aes(x   = third_most_frequent_stars,
           y   = avg_rating))+ 
  geom_point(size = 3) +
  geom_hline(yintercept = avg_rating_mean, linetype = "dashed", color = "red", size = 1.2) + 
  labs(y = "Average Rating", x = "Third Most Frequent Stars") +
  theme_minimal() 
```
```{r}
avg_numberofrating_mean <- mean(df2$num_ratings, na.rm = TRUE)

ggplot(data    = df2,
       aes(x   = third_most_frequent_stars,
           y   = num_ratings))+ 
  geom_point(size = 3) +
  geom_hline(yintercept = avg_numberofrating_mean, linetype = "dashed", color = "blue", size = 1.2) + 
  labs(y = "Average Number of Ratings", x = "Third Most Frequent Stars (100k)") +
  theme_minimal() +
  scale_y_continuous(labels = function(x) x / 1000,  # Divide by 100,000 to adjust the unit
                     breaks = scales::pretty_breaks(n = 10)) +
  theme(axis.text.y = element_text(hjust = 1.5)) + 
  annotate("text", x = 1.6, y = avg_numberofrating_mean, 
           label = paste("Average Number of Ratings:", round(avg_numberofrating_mean, 2)), 
           hjust = -0.1, vjust = -1.5, color = "blue", fontface = "bold")
```

```{r}
df2$num_pictures_iphone
```

```{r, fig.width=5, fig.height=10}
iphone <- ggplot(data = df2, 
       aes(third_most_frequent_stars, 
           fill = as.factor(num_pictures_iphone))) + 
       geom_bar(position = "fill") + 
       labs(x = "", y = "Percentage (fill)", fill = 'iPhone Screenshots') + fill_palette("Pastel1")

ipad <- ggplot(data = df2, 
       aes(third_most_frequent_stars, 
           fill = as.factor(num_pictures_ipad))) + 
       geom_bar(position = "fill") + 
       labs(x = "", y = "Percentage (fill)", fill = 'iPad Screenshots') + fill_palette("Pastel1")

watch <- ggplot(data = df2, 
       aes(third_most_frequent_stars, 
           fill = as.factor(num_pictures_watch))) + 
       geom_bar(position = "fill") + 
       labs(x = "", y = "Percentage (fill)", fill = 'Apple Watch Screenshots') + fill_palette("Pastel1")

ggarrange(
    iphone, ipad, watch,
    labels = c("iPhone", "iPad", "Apple Watch"),
    ncol = 1,
    nrow = 3
    
) 
```

```{r}
df2 %>% count(theme_color)
```




$ date_collection            <chr> "2024-10-29", "2024-10-29", "2024-10-29", "2024-10-29", "2024-10-29"
$ appname                    <chr> "CIBC Mobile Banking", "TD Canada", "Scotiabank", "BMO Mobile Banking", "RBC Mobile"
$ category                   <chr> "Finance", "Finance", "Finance", "Finance", "Finance"
$ headline                   <chr> "Everyday banking on the go", "Bank on the go with the TD app", "Designed for real …
$ theme_color                <chr> "red", "green", "red", "blue", "blue"
$ name_in_icon               <fct> 1, 1, 0, 0, 0
$ chart_rank                 <int> 4, 5, 7, 10, 3
$ avg_rating                 <dbl> 4.2, 4.5, 4.7, 4.6, 4.8
$ num_ratings                <int> 21000, 79200, 761500, 111300, 208900
$ age_min                    <int> 4, 4, 4, 4, 4
$ price                      <chr> "free", "free", "free", "free", "free"
$ num_pictures_iphone        <int> 8, 10, 8, 4, 10
$ num_pictures_ipad          <int> 3, 10, 5, 3, 10
$ num_pictures_watch         <int> 4, 4, 3, 0, 4
$ developer                  <chr> "CIBC", "TD", "Scotiabank", "BMO Financial Group", "Royal Bank of Canada"
$ language                   <chr> "['EN', 'FR']", "['EN', 'FR', 'SCH', 'TCH']", "['EN', 'FR']", "['EN', 'FR']", "['EN…
$ size                       <dbl> 140.7, 328.2, 193.3, 124.6, 583.7
$ device_compatible          <chr> "['iphone', 'ipad', 'apple watch']", "['iphone', 'ipad', 'apple watch']", "['iphone…
$ most_frequent_stars        <fct> 5, 5, 5, 5, 5
$ second_most_frequent_stars <fct> 4, 4, 4, 4, 4
$ third_most_frequent_stars  <fct> 1, 1, 3, 1, 3
$ update_info                <chr> "2024-09-26", "2024-10-21", "2024-10-18", "2024-09-19", "2024-10-08"
$ version                    <chr> "10.57.3", "24.09", "2409.0.3", "6.12.0", "6.46"
$ data_gathered              <chr> "['purchases', 'search history', 'usage data', 'location', 'sensitive info', 'ident…
$ apple_watch                <fct> 1, 1, 1, 0, 1
$ apple_wallet               <fct> 1, 1, 1, 1, 1
$ youmightlike               <chr> "['Neo Financial', 'Borrowel: Credit Report', 'TD Insurance', 'Western Union Send M…
$ summary                    <chr> "FIND IMPORTANT DISCLOSURES BELOW. The CIBC Mobile Banking App has received the hig…
$ url_link                   <chr> "https://apps.apple.com/ca/app/cibc-mobile-banking/id351448953", "https://apps.appl…
$ Bank                       <chr> "CIBC", "TD", "Scotia", "BMO", "RBC"
$ weighted_average












